Ancestry linkage in hybrid zones

### 2016-01-25 drafts/hybrid_zone.tex
made code and plot for statistics

\subsection{}

@@

>>>>

@@

\subsection{Statistics}
With the above theory and simulations, we are able to make predictions about patterns surrounding selected loci. In reality, however, such loci are not known, so it is useful to have per-site statistics that may allow for detection of candidate targets of selection. The most straightforward measure is $l_I(b)$ the length of haplotype chunk that a sampled chunk containing genomic position $b$, conditioned on ancestry $I$ at the site.

Another statistic is the cumulative probability $C_I(b)$ of a sampled chunk encompassing position $b$ being longer than a chunk sampled from the distribution of all chunk lengths across the genome in the population.

Additionally, we look at the mean value of these statistics in the two chunks, $b-$ and $b+$, that flank the one containing $b$.
